Macroscopic Salt Rejection through Electrostatically Gated Monolayer Porous Graphene

### 2018-10-03 paper/paper.tex
Complete refs in main

\documentclass[manuscript=letter, email=true, hyperref=true, keywords=false]{achemso}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{times}
\usepackage{todonotes}
% \usepackage{lineno}
% \linenumbers

@@

Figure \ref{fig:1}a depicts the experimental setup characterizing
ionic diffusion through a sheet of monolayer porous graphene (PG). Two
reservoirs, namely the high-concentration reservoir (HCR) containing
electrolyte solution with molar concentration $c_0$, and the
low-concentration reservoir (LCR) containing de-ionized (DI) water,
are separated by a PG membrane supported by polycarbonate track-etched
(PCTE) film. Magnetic stirrers are used to minimize the effects of
external concentration polarization, and a conductivity probe is
placed in the LCR to monitor the ionic concentration as a function of
time. The membrane is attached to a piece of copper tape connected to
a voltage source applying an electrical bias $V_{\mathrm{G}}$, with
the LCR grounded (Figure \ref{fig:1}a inset). We fabricated the
PCTE-supported PG using the protocol developed by our group
\cite{Choi_2018}, as schematically shown in Figure \ref{fig:1}b. The
normally distributed, circular pores with pore diameters of 20$\pm$10
nm (Figure \ref{fig:1}c inset) over a large area were drilled on
graphene.  By optimizing the subsequent transfer process, a high
surface coverage (> 98\%) of graphene on PCTE was reached (Figure
\ref{fig:1}c), allowing to reliably characterize the ion transport
behavior (details see Supplementary Information Section S1).  The
system presented here allows us to systematically investigate the
diffusive flux across a sheet of porous graphene, $\boldsymbol{J}$,
driven by the gradient of electrochemical potential in the electrolyte
medium.

First, the control experiments were carried out by measuring the ionic
diffusion of seven salt species, including KCl, NaCl, LiCl,
K$_{2}$SO$_{4}$, MgSO4$_{4}$, CaCl$_{2}$ and K$_{3}$Fe(CN)$_{6}$,
through the bare PCTE membrane at $c_{0}$ = 0.1 mM. As the diffusive
flux is comparably small, the conductivity versus time profile
(e.g. Figure \ref{fig:2}a) remains linear within the measurement
duration (1 h), suggesting the concentration change in individual
reservoirs is negligible \todo[inline]{really?}. The diffusive fluxes
correspond to different salts were obtained by converting the
conductivity-time profiles with the calibration curves (blue bars in
Figure \ref{fig:2}b and Supplementary Figure S2). For comparison
purposes, based on the assumption that the membrane consists
cylindrical pores with uniform diameter and a low tortuosity $\tau$ of
$\sim{}$1.2 \cite{O_Hern_2012}, the molar diffusive flux through
the bare PCTE membrane, $\boldsymbol{J}_{\mathrm{PCTE}}$, follows:
  \begin{equation}
    \label{eq:j-pcte}
    \boldsymbol{J}_{\mathrm{PCTE}} = \frac{\pi a^{2} N_{\mathrm{p}} D \Delta c}{\delta \tau}
  \end{equation}
where $a$ is the PCTE pore radius, $N_{\mathrm{p}}$ is numbers of pore
per area, $D$ is the salt diffusivity, and $\Delta c$ is the bulk
concentration difference between two reservoirs, i.e.,
$\Delta c \sim c_{0}$, $\delta$ is the thickness of the PCTE membrane,
and $\tau$ is the tortuosity. By using the salt diffusivity values
provided by the PTCE vendor (Supplementary Table S1), the
calculated diffusive fluxes (red bars in Figure \ref{fig:2}b) show
reasonable agreement with the experimental values.

Next, we carried out the same experiments using the PG-covered PCTE
membrane (PG-PCTE), without electrostatic gating. The measured
diffusive flux values, $\boldsymbol{J}_{\mathrm{PG0}}$ (green bars in
Figure \ref{fig:2}b), remain at the same order of magnitude compared
to those of bare PCTE membrane, suggesting that the mass transfer
resistance of PG is not significant, as the permeability is high. We
observed a more pronounced decrease of diffusive flux in KCl,
K$_{2}$SO$_{4}$ and K$_{3}$Fe(CN)$_{6}$ systems but not for the rest
of the salts. We hypothesized that the strong cation-$\pi$ interactions
between K$^{+}$ cations and graphene slow down the migration of cations
along the surface-mediated transport pathway \cite{Sun_2014}.

@@

We next discuss the effects of electrostatic gating on graphene. In
order to avoid any interference from the conductivity probe to the
membrane potential, the “three-interval” method, which had been used
in controlling the membrane potential in mesoporous carbon membranes
\cite{Surwade_2014}, is adopted here. Figure \ref{fig:2}a presents the
representative data of the measured conductivity with respect to
time. Specifically, in the first interval, the gate voltage source is
turned off and the conductivity probe is on, allowing us to obtain the
conductivity-time profile corresponding to the diffusive flux through
the PG-PCTE membrane, giving the average slope $s_{1}$. In the second
interval, a voltage $V_{\mathrm{G}}$ is applied to the membrane after
turning off the conductivity probe, followed by the third interval, in
which the conductivity probe is turned on again to give the
corresponding slope, $s_{3}$. The slope corresponding to the second
interval, $s_{2}$, as the conductivity probe is off, is determined by
linearly interpolating the conductivities from the endpoint of
interval 1 to the starting point of interval 3. Accordingly, we define
the salt rejection factor, $\xi$, which is effectively equivalent to
the relative degree of diffusive flux decrease as follows:
\begin{equation}
  \label{eq:rejection}
  \xi = \frac{\bar{s} - s_{2}}{\bar{s}} = \frac{\boldsymbol{J}_{\mathrm{PG0}}
    - \boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})}{\boldsymbol{J}_{\mathrm{PG0}}}
\end{equation}
where $\bar{s}$ is the average slope of $s_{1}$ and $s_{3}$, namely
$(s_{1} + s_{3})/2$, and
$\boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})$ is the diffusive flux
across the PTCE-supported PG double layer as a function of
$V_{\mathrm{G}}$. Note that a positive $\xi$ between 0 and 1
represents a decrease of the diffusive flux. The factor $\xi$ enables
a reliable and stable measurement of salt rejection, as the salt
species and initial conditions may induce a degree of measurement
uncertainty between different samples. A control experiment was
performed to ensure the copper tape was not in direct contact with the
ionic solution (Supplementary Section 3).

Using 0.1 mM KCl solution in HCR, we measured $\xi$ as a function of
$V_{\mathrm{G}}$ within $\pm1.25$ V, before triggering the
electrochemical reactions (Figure \ref{fig:2}c). We observe an
asymmetric dependence of $\xi$ with respect to $V_{\mathrm{G}}$, with
a higher degree of salt rejection for $V_{\mathrm{G}}>0$. where
positive carriers (holes) are induced in graphene. We notice that an
increase $\xi$, or a decrease of $\boldsymbol{J}_{\mathrm{PG}}$ with
$V_{\mathrm{G}}$, showing an inverse trend compared to those observed
in ionic field effect transistors (IFETs), in which the diffusive flux
increases with the gate voltage \cite{Nam_2009,Cheng_2018}. A further
increase of the KCl concentration $c_{0}$ influences the attainable
degree of salt rejection. $\xi$ values measured at
$V_{\mathrm{G}}$=1.25 V, $\xi_{\mathrm{max}}$, as a function of
$c_{0}$ from 10$^{-4}$ to 10$^{-2}$ M KCl (see Supplementary Section
S4) exhibit a power law dependency (Figure \ref{fig:2}d). The
$\xi_{\mathrm{max}}-c_{0}$ relation can be nicely fitted by a power
law function following
$\xi_{\mathrm{max}} c_{0}^{0.59} = \mathrm{Constant}$. As the Debye
screening length in solution, $\lambda_{\mathrm{D}}$, is inversely
proportional to $c^{0.5}$, we infer that the $V_{\mathrm{G}}$-induced
salt rejection originates from the modulation of the electrical double
layer (EDL), as will be discussed later.

@@

  \nabla \cdot \boldsymbol{J}_{i} = -\Delta \cdot (\frac{D_{i}}{k_{\mathrm{B}}T} c_{i} N_{\mathrm{A}} \nabla \mu_{i}) = 0

@@

graphene quantum capacitance effect\cite{Xia_2009} (Figure

@@

graphene coincides with the Dirac point at $V_{\mathrm{G}}=0$, the elementary

@@

velocity of graphene (more details find Supplementary Section SXX
\todo{ref}). Note that the PG film fabricated experimentally is
double-layer turbostratic graphene, in which we assume the

@@

graphene (Eq. \ref{eq:delta-phiG}). However, for chemical vapor
deposition- (CVD) synthesized graphene used in our experiments, it is

@@

during synthesis and patterning \cite{Dean_2010}, effectively
increasing the graphene quantum capacitance for $V_{\mathrm{G}}<0$
(Supplementary Figure SXX \todo{ref}). With the nonideality in mind,
hereafter, we compare the calculations and experiments in the regime
of $V_{\mathrm{G}}>0$. For example, Figure \ref{fig:3}c presents the
calculated $\sigma_{\mathrm{G}}$ and $\psi_{\mathrm{G}}$ as a function
of $V_{\mathrm{G}}$ considering the ionic diffusion through a single
20 nm-diameter nanopore drilled on a sheet of semi-infinite double
layer graphene that separates HCR containing KCl solution at
$c_{0}=0.1$ mM, and LCR at $c_{0}/10$ in axisymmetric coordinates
(details see Supplementary Section SXX \todo{cite}). Indeed, the

@@

$\psi_{\mathrm{G}}$ tp $\sim$0.3 V at $V_{\mathrm{G}}$=1.25 V,

@@

\subsection{Salt rejection mechanism}
\label{sec:mechanism}
The numerical procedure described above allows us to resolve the
concentration and electric potential profiles near to a graphene
nanopore for a given $V_{\mathrm{G}}$. Since the ionic flux is driven
by both $\psi$ and $c$ fields (see Eq. \ref{eq:pnp} and \ref{eq:mu}),
we focus on the electrochemical potential $\mu_{i}$, which represents
the combined driving force, to reveal its dependence on the applied
$V_{\mathrm{G}}$. Following the same system considered in Figure
\ref{fig:3}b, the calculated axisymmetric electric potential $\psi$
and the relative electrochemical potentials,
$\Delta \mu_{\mathrm{K^{+}}}$ and $\Delta \mu_{\mathrm{Cl^{-}}}$, for
$V_{\mathrm{G}}$=0.75 V are shown in Figure \ref{fig:4}a and
\ref{fig:4}b, respectively. The reference point of the electrochemical
potentials is set at the bulk phase in the HCR. As expected, the
electric potential reaches the maximum at the graphene surface (with
$\psi_{\mathrm{G}}$ of $\sim$100 mV) and decays towards the bulk
solution phase, forming an EDL surrounding the graphene surface. Since
the Debye screening length $\lambda_{\mathrm{D}}$ is comparable to the
pore radius $R_{\mathrm{G}}$, the electric potential at the nanopore
center remains at $\sim$25 mV, comparable to the thermal energy at
room temperature ($k_{\mathrm{B}}T=$26 meV). Consequently, it is
evident that the potential barrier is sufficient to modulate the
diffusive flux.

We further reveal the cation and anion transport pathways by looking
into their electrochemical potentials (Figure \ref{fig:4}b). By
increasing $V_{\mathrm{G}}$, a more positive $\psi_{\mathrm{G}}$ on
graphene surface reduces the cation concentration at the pore edge due
to the electrostatic interactions, thereby increasing its
concentration gradient at the pore center. On the other hand, the
anion concentration near the pore edge increases exponentially, such
that the concentration gradient at the pore center becomes
small. (also see Supplementary Figures SXX \todo{note}). We also
observe that $\Delta \mu_{+}$ is dominated by the concentration, while
$\Delta \mu_{-}$ is much less than $\Delta \mu_{+}$ due to the balance
between the diffusion and drift potentials (see Supplementary Figure
SXX \todo{note}). The observations confirm the distinct ionic
transport pathways upon applying a positive $V_{\mathrm{G}}$: pore
center for cations and pore edge for anions. Figure \ref{fig:4}c
presents the calculated z-component of the cation and anion fluxes
through the pore at the graphene plane (z = 0), $\boldsymbol{J}_{z}$
,as a function of the normalized radius, $r/R_{\mathrm{G}}$ , where
$r$ is the radial coordinate and $R_{\mathrm{G}}$ is the pore radius,
at different $V_{\mathrm{G}}$ values. Note that $\boldsymbol{J}_{z}$
is negative because the LCR is placed at z < 0 in the simulations. At
$V_{\mathrm{G}}=$0 (pure diffusion), the anion and cation flux
profiles are identical, with a higher flux near the pore edge, which
is expected, as the concentration gradient is higher. By gradually
increasing $V_{\mathrm{G}}$, both fluxes are reduced throughout the
pore, while the degree of reduction is more pronounced at the pore
edge for the cation, and at the pore center for the anion, following
the scenarios we discussed above. Accordingly, the integrated fluxes
across the pore, $|\boldsymbol{J}_{z}|$, are reduced with
$V_{\mathrm{G}}$ (Figure \ref{fig:4}d). A total flux reduction of up
to 80\% is predicted. Another interesting finding here is that, by
increasing $V_{\mathrm{G}}$, the nanopore transport preferentially
allows cations over anions, or in other words, the anion flux is more
reduced with $V_{\mathrm{G}}$ (see Figure \ref{fig:4}c), known as the
ion selectivity of graphene nanopore \cite{Rollings_2016}.

The above mechanistic findings, nevertheless, do not fully clarify the
experimentally observed reduction of diffusive flux upon
gating. Indeed, the same physical mechanism also governs the ionic
transport through an IFET, in which a nonzero electric potential at
the nanopore center usually results in an increase of ionic
conductivity \cite{Nam_2009,Lee_2015,Feng_2016}. To this end, we
further increased the graphene surface potential $\psi_{\mathrm{G}}$
considering the same system (Supplementary Section 6
\todo{confirm}). Intriguingly, by increasing $\psi_{\mathrm{G}}$
larger than 400 mV, the ionic flux starts to increase, reversing the
trend observed at the low $\psi_{\mathrm{G}}$ regime, because of an
increase of cation diffusion \todo{note!}. This level of
$\psi_{\mathrm{G}}$ cannot be reached experimentally in graphene
membrane, as this requires a $V_{\mathrm{G}}$ larger than 2.0 V
\todo{confirm}, which triggers the electrochemical reactions. On the
other hand, in an IFET, the electric potential on the pore wall is
considerably higher, equivalent to $V_{\mathrm{G}}$ due to the
metallic nature of gate electrode (having an infinitely-large quantum
capacitance). We therefore conclude that the quantum
capacitance-induced nonlinear damping in the surface potential results
in the observed salt rejection.  Following the above discussions, we
further investigate the physical limits for the biased graphene
nanopores. Specifically, the salt rejection characteristics are
controlled by: (i) the overlap of EDL inside the nanopore, essentially
controlled by two length scales of $\lambda_{\mathrm{D}}$ and
$R_{\mathrm{G}}$, and (ii) the graphene surface potential
$\psi_{\mathrm{G}}$ controlled by $V_{\mathrm{G}}$ following
Eq. \ref{eq:Vg}. To this end, we calculate $\psi_{\mathrm{G}}$ as a
function of $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and
$V_{\mathrm{G}}$ (Figure \ref{fig:5}a). Clearly, when the bulk
concentration $c_{0}$ increases, a higher $V_{\mathrm{G}}$ is required
to reach the same level of $\psi_{\mathrm{G}}$. Consequently, as
revealed in Figure \ref{fig:5}b, the calculated salt rejection factor
$\xi$ increases with both $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and
$V_{\mathrm{G}}$, in line with the experimentally observed
$\xi - c_{0}$ dependence. We also find the overall trends for
$\psi_{\mathrm{G}}$ and $\xi$ with respect to
$\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
similar. More importantly, based on our theoretical prediction, with
$V_{\mathrm{G}}$=1.25 V and
$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$=1.0, a high value of $\xi$ of
$>$0.85 can be achieved.

@@

In summary, we have
presented a comparative experimental and modeling study on macroscopic
salt rejection through a sheet of large-area porous graphene under
electrostatic gating. We show that due to a small quantum capacitance
of double layer graphene, the graphene surface potential is
considerably lower than the applied gate voltage. As a result, the
subtle redistribution of the electrochemical potentials create new
pathways for ionic transport, which in turn lead to a considerably
degree of salt rejection. We report a high degree of salt rejection at
$V_{\mathrm{G}}$=1.25 V of up to 55\% and 80\%, based on our
experiments and theoretical predictions, respectively. We demonstrate
that the observed salt rejection positively correlates with the Debye
screening length that nonlinearly modulates the graphene surface
potential and charge density. The experimental results and fundamental
principles presented here open an avenue towards realization of
atomically thin 2D porous membranes for advanced separation process in
electrolyte solutions.

@@

\section{Acknowledgements}
\label{sec:ack}
\todo[inline]{TBD} R.M.W. and H.G.P. acknowledge the support from
XXX. T.T. and C.J.S. are grateful for the financial support from the
ETH startup funding.

@@

H.G.P and C.J.S conceived the experiments. R.M.W measured the ion diffusion
and gating experiments. T.T performed numerical simulations. All authors
contributed to writing and discussion.

>>>>

\documentclass[journal=langd5,email=true, hyperref=true, keywords=false]{achemso}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{times}
\usepackage{todonotes}
\newcommand{\Fig}{Fig.}
% \usepackage{lineno}
% \linenumbers

@@

\Fig{} \ref{fig:1}a depicts the experimental setup characterizing
ionic diffusion through a sheet of monolayer porous graphene (PG). Two
reservoirs, namely the high-concentration reservoir (HCR) containing
electrolyte solution with molar concentration $c_0$, and the
low-concentration reservoir (LCR) containing de-ionized (DI) water,
are separated by a PG membrane supported by polycarbonate track-etched
(PCTE) film. Magnetic stirrers are used to minimize the effects of
external concentration polarization, and a conductivity probe is
placed in the LCR to monitor the ionic concentration as a function of
time. The membrane is attached to a piece of copper tape connected to
a voltage source applying an electrical bias $V_{\mathrm{G}}$, with
the LCR grounded (\Fig{} \ref{fig:1}a inset). We fabricated the
PCTE-supported PG using the protocol developed by our group
\cite{Choi_2018}, as schematically shown in \Fig{} \ref{fig:1}b. The
normally distributed, circular pores with pore diameters of 20$\pm$10
nm (\Fig{} \ref{fig:1}c inset) over a large area were drilled on
graphene.  By optimizing the subsequent transfer process, a high
surface coverage ($>$ 98\%) of graphene on PCTE was reached (\Fig{}
\ref{fig:1}c), allowing to reliably characterize the ion transport
behavior (details see Supplementary Information Section S1).  The
system presented here allows us to systematically investigate the
diffusive flux across a sheet of porous graphene, $\boldsymbol{J}$,
driven by the gradient of electrochemical potential in the electrolyte
medium.

First, the control experiments were carried out by measuring the ionic
diffusion of seven salt species, including KCl, NaCl, LiCl,
K$_{2}$SO$_{4}$, MgSO4$_{4}$, CaCl$_{2}$ and K$_{3}$Fe(CN)$_{6}$,
through the bare PCTE membrane at $c_{0}$ = 0.1 mM. As the diffusive
flux is comparably small, the conductivity versus time profile
(e.g. \Fig{} \ref{fig:2}a) remains linear within the measurement
duration (1 h), suggesting the concentration change in individual
reservoirs is negligible \todo[inline]{Isn't the increasing of
  conductivity a measure of the diffusion of ions?}. The diffusive fluxes
correspond to different salts were obtained by converting the
conductivity-time profiles with the calibration curves (blue bars in
\Fig{} \ref{fig:2}b and Supplementary \Fig{} S2). For comparison
purposes, based on the assumption that the membrane consists
cylindrical pores with uniform diameter and a low tortuosity $\tau$ of
$\sim{}$1.2 \cite{O_Hern_2012}, the molar diffusive flux through the
bare PCTE membrane, $\boldsymbol{J}_{\mathrm{PCTE}}$, follows:
  \begin{equation}
    \label{eq:j-pcte}
    \boldsymbol{J}_{\mathrm{PCTE}} = \frac{\pi a^{2} N_{\mathrm{p}} D \Delta c}{\delta \tau}
  \end{equation}
where $a$ is the PCTE pore radius, $N_{\mathrm{p}}$ is numbers of pore
per area, $D$ is the salt diffusivity, and $\Delta c$ is the bulk
concentration difference between two reservoirs, i.e.,
$\Delta c \sim c_{0}$, $\delta$ is the thickness of the PCTE membrane,
and $\tau$ is the tortuosity. By using the salt diffusivity values
provided by the PTCE vendor (Supplementary Table S1), the
calculated diffusive fluxes (red bars in \Fig{} \ref{fig:2}b) show
reasonable agreement with the experimental values.

Next, we carried out the same experiments using the PG-covered PCTE
membrane (PG-PCTE), without electrostatic gating. The measured
diffusive flux values, $\boldsymbol{J}_{\mathrm{PG0}}$ (green bars in
\Fig{} \ref{fig:2}b), remain at the same order of magnitude compared
to those of bare PCTE membrane, suggesting that the mass transfer
resistance of PG is not significant, as the permeability is high. We
observed a more pronounced decrease of diffusive flux in KCl,
K$_{2}$SO$_{4}$ and K$_{3}$Fe(CN)$_{6}$ systems but not for the rest
of the salts. We hypothesized that the strong cation-$\pi$ interactions
between K$^{+}$ cations and graphene slow down the migration of cations
along the surface-mediated transport pathway \cite{Sun_2014}.

@@

We next discuss the effects of electrostatic gating on graphene. In
order to avoid any interference from the conductivity probe to the
membrane potential, the “three-interval” method, which had been used
in controlling the membrane potential in mesoporous carbon membranes
\cite{Surwade_2014}, is adopted here. \Fig{} \ref{fig:2}a presents the
representative data of the measured conductivity with respect to
time. Specifically, in the first interval, the gate voltage source is
turned off and the conductivity probe is on, allowing us to obtain the
conductivity-time profile corresponding to the diffusive flux through
the PG-PCTE membrane, giving the average slope $s_{1}$. In the second
interval, a voltage $V_{\mathrm{G}}$ is applied to the membrane after
turning off the conductivity probe, followed by the third interval, in
which the conductivity probe is turned on again to give the
corresponding slope, $s_{3}$. The slope corresponding to the second
interval, $s_{2}$, as the conductivity probe is off, is determined by
linearly interpolating the conductivities from the endpoint of
interval 1 to the starting point of interval 3. Accordingly, we define
the salt rejection factor, $\xi$, which is effectively equivalent to
the relative degree of diffusive flux decrease as follows:
\begin{equation}
  \label{eq:rejection}
  \xi = \frac{\bar{s} - s_{2}}{\bar{s}} = \frac{\boldsymbol{J}_{\mathrm{PG0}}
    - \boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})}{\boldsymbol{J}_{\mathrm{PG0}}}
\end{equation}
where $\bar{s}$ is the average slope of $s_{1}$ and $s_{3}$, namely
$(s_{1} + s_{3})/2$, and
$\boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})$ is the diffusive flux
across the PTCE-supported PG double layer as a function of
$V_{\mathrm{G}}$. Note that a positive $\xi$ between 0 and 1
represents a decrease of the diffusive flux. The factor $\xi$ enables
a reliable and stable measurement of salt rejection, as the salt
species and initial conditions may induce a degree of measurement
uncertainty between different samples. A control experiment was
performed to ensure the copper tape was not in direct contact with the
ionic solution (Supplementary Section 3).

Using 0.1 mM KCl solution in HCR, we measured $\xi$ as a function of
$V_{\mathrm{G}}$ within $\pm1.25$ V, before triggering the
electrochemical reactions (\Fig{} \ref{fig:2}c). We observe an
asymmetric dependence of $\xi$ with respect to $V_{\mathrm{G}}$, with
a higher degree of salt rejection for $V_{\mathrm{G}}>0$. where
positive carriers (holes) are induced in graphene. We notice that an
increase $\xi$, or a decrease of $\boldsymbol{J}_{\mathrm{PG}}$ with
$V_{\mathrm{G}}$, showing an inverse trend compared to those observed
in ionic field effect transistors (IFETs), in which the diffusive flux
increases with the gate voltage \cite{Nam_2009,Cheng_2018}. A further
increase of the KCl concentration $c_{0}$ influences the attainable
degree of salt rejection. $\xi$ values measured at
$V_{\mathrm{G}}$ = 1.25 V, $\xi_{\mathrm{max}}$, as a function of
$c_{0}$ from 10$^{-4}$ to 10$^{-2}$ M KCl (see Supplementary Section
S4) exhibit a power law dependency (\Fig{} \ref{fig:2}d). The
$\xi_{\mathrm{max}}-c_{0}$ relation can be nicely fitted by a power
law function following
$\xi_{\mathrm{max}} c_{0}^{0.59} = \mathrm{Constant}$. As the Debye
screening length in solution, $\lambda_{\mathrm{D}}$, is inversely
proportional to $c^{0.5}$, we infer that the $V_{\mathrm{G}}$-induced
salt rejection originates from the modulation of the electrical double
layer (EDL), as will be discussed later.

@@

  \nabla \cdot \boldsymbol{J}_{i} = -\nabla \cdot (\frac{D_{i}}{k_{\mathrm{B}}T} c_{i} N_{\mathrm{A}} \nabla \mu_{i}) = 0

@@

graphene quantum capacitance effect\cite{Xia_2009} (\Fig{}

@@

graphene coincides with the Dirac point at $V_{\mathrm{G}}$ = 0, the elementary

@@

velocity of graphene (more details find Supplementary Section
S5). Note that the PG film fabricated experimentally is double-layer
turbostratic graphene, in which we assume the

@@

graphene (Eq. \ref{eq:delta-phiG}). However, for graphene synthesized
by chemical vapor deposition (CVD) used in our experiments, it is

@@

during synthesis and patterning \cite{Dean_2010}, effectively reducing
the charge density and surface potential on graphene
$V_{\mathrm{G}}<0$ (Supplementary \Fig{} S3). With the nonideality in
mind, hereafter, we compare the calculations and experiments in the
regime of $V_{\mathrm{G}}>0$. For example, \Fig{} \ref{fig:3}c
presents the calculated $\sigma_{\mathrm{G}}$ and $\psi_{\mathrm{G}}$
as a function of $V_{\mathrm{G}}$ considering the ionic diffusion
through a single 20 nm-diameter nanopore drilled on a sheet of
semi-infinite double layer graphene that separates HCR containing KCl
solution at $c_{0}$ = 0.1 mM, and LCR at $c_{0}/10$ in axisymmetric
coordinates (details see Supplementary Section S5). Indeed, the

@@

$\psi_{\mathrm{G}}$ tp $\sim$0.3 V at $V_{\mathrm{G}}$ = 1.25 V,

@@

\subsection{Salt rejection mechanism}
\label{sec:mechanism}
The numerical procedure described above allows us to resolve the
concentration and electric potential profiles near to a graphene
nanopore for a given $V_{\mathrm{G}}$. Since the ionic flux is driven
by both $\psi$ and $c$ fields (see Eq. \ref{eq:pnp} and \ref{eq:mu}),
we focus on the electrochemical potential $\mu_{i}$, which represents
the combined driving force, to reveal its dependence on the applied
$V_{\mathrm{G}}$. Following the same system considered in \Fig{}
\ref{fig:3}b, the calculated axisymmetric electric potential $\psi$
and the relative electrochemical potentials,
$\Delta \mu_{\mathrm{K^{+}}}$ and $\Delta \mu_{\mathrm{Cl^{-}}}$, for
$V_{\mathrm{G}}$ = 0.75 V are shown in \Fig{} \ref{fig:4}a and
\ref{fig:4}b, respectively. The reference point of the electrochemical
potentials is set at the bulk phase in the HCR. As expected, the
electric potential reaches the maximum at the graphene surface (with
$\psi_{\mathrm{G}}$ of $\sim$100 mV) and decays towards the bulk
solution phase, forming an EDL surrounding the graphene surface. Since
the Debye screening length $\lambda_{\mathrm{D}}$ is comparable to the
pore radius $R_{\mathrm{G}}$, the electric potential at the nanopore
center remains at $\sim$25 mV, comparable to the thermal energy at
room temperature ($k_{\mathrm{B}}T$ = 26 meV). Consequently, it is
evident that the potential barrier is sufficient to modulate the
diffusive flux.

We further reveal the cation and anion transport pathways by looking
into their electrochemical potentials (\Fig{} \ref{fig:4}b). By
increasing $V_{\mathrm{G}}$, a more positive $\psi_{\mathrm{G}}$ on
graphene surface reduces the cation concentration at the pore edge due
to the electrostatic interactions, thereby increasing its
concentration gradient at the pore center. On the other hand, the
anion concentration near the pore edge increases exponentially, such
that the concentration gradient at the pore center becomes
small. (also see Supplementary \Fig{}s S4). We also
observe that $\Delta \mu_{+}$ is dominated by the concentration, while
$\Delta \mu_{-}$ is much less than $\Delta \mu_{+}$ due to the balance
between the diffusion and drift potentials (see Supplementary \Fig{}
S5). The observations confirm the distinct ionic
transport pathways upon applying a positive $V_{\mathrm{G}}$: pore
center for cations and pore edge for anions. \Fig{} \ref{fig:4}c
presents the calculated z-component of the cation and anion fluxes
through the pore at the graphene plane (z = 0), $\boldsymbol{J}_{z}$
,as a function of the normalized radius, $r/R_{\mathrm{G}}$ , where
$r$ is the radial coordinate and $R_{\mathrm{G}}$ is the pore radius,
at different $V_{\mathrm{G}}$ values. Note that $\boldsymbol{J}_{z}$
is negative because the LCR is placed at z < 0 in the simulations. At
$V_{\mathrm{G}}$ = 0 (pure diffusion), the anion and cation flux
profiles are identical, with a higher flux near the pore edge, which
is expected, as the concentration gradient is higher. By gradually
increasing $V_{\mathrm{G}}$, both fluxes are reduced throughout the
pore, while the degree of reduction is more pronounced at the pore
edge for the cation, and at the pore center for the anion, following
the scenarios we discussed above. Accordingly, the integrated fluxes
across the pore, $|\boldsymbol{J}_{z}|$, are reduced with
$V_{\mathrm{G}}$ (\Fig{} \ref{fig:4}d). A total flux reduction of up
to 80\% is predicted. Another interesting finding here is that, by
increasing $V_{\mathrm{G}}$, the nanopore transport preferentially
allows cations over anions, or in other words, the anion flux is more
reduced with $V_{\mathrm{G}}$ (see \Fig{} \ref{fig:4}c), known as the
ion selectivity of graphene nanopore \cite{Rollings_2016}.

The above mechanistic findings, nevertheless, do not fully clarify the
experimentally observed reduction of diffusive flux upon
gating. Indeed, the same physical mechanism also governs the ionic
transport through an IFET, in which a nonzero electric potential at
the nanopore center usually results in an increase of ionic
conductivity \cite{Nam_2009,Lee_2015,Feng_2016}. To this end, we
further increased the graphene surface potential $\psi_{\mathrm{G}}$
considering the same system (Supplementary Section 6). Intriguingly,
by increasing $\psi_{\mathrm{G}}$ larger than 400 mV, the ionic flux
starts to increase, reversing the trend observed at the low
$\psi_{\mathrm{G}}$ regime, due to (i) the drift flux become dominant
over diffusion flux and (ii) the concentration near the pore edge
(prefered path) greatly increases. This level of $\psi_{\mathrm{G}}$
cannot be reached experimentally in graphene membrane, as this
requires a $V_{\mathrm{G}}$ larger than 2.0 V, which triggers the
electrochemical reactions \cite{Toh_2011}. On the other hand, in an
IFET, the electric potential on the pore wall is considerably higher,
equivalent to $V_{\mathrm{G}}$ due to the metallic nature of gate
electrode (having an infinitely-large quantum capacitance). We
therefore conclude that the quantum capacitance-induced nonlinear
damping in the surface potential results in the observed salt
rejection.  Following the above discussions, we further investigate
the physical limits for the biased graphene nanopores. Specifically,
the salt rejection characteristics are controlled by: (i) the overlap
of EDL inside the nanopore, essentially controlled by two length
scales of $\lambda_{\mathrm{D}}$ and $R_{\mathrm{G}}$, and (ii) the
graphene surface potential $\psi_{\mathrm{G}}$ controlled by
$V_{\mathrm{G}}$ following Eq. \ref{eq:Vg}. To this end, we calculate
$\psi_{\mathrm{G}}$ as a function of
$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ (\Fig{}
\ref{fig:5}a). Clearly, when the bulk concentration $c_{0}$ increases,
a higher $V_{\mathrm{G}}$ is required to reach the same level of
$\psi_{\mathrm{G}}$. Consequently, as revealed in \Fig{} \ref{fig:5}b,
the calculated salt rejection factor $\xi$ increases with both
$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and $V_{\mathrm{G}}$, in line
with the experimentally observed $\xi - c_{0}$ dependence. We also
find the overall trends for $\psi_{\mathrm{G}}$ and $\xi$ with respect
to $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
similar. More importantly, based on our theoretical prediction, with
$V_{\mathrm{G}}$ = 1.25 V and $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$
= 1.0, a high value of $\xi$ of $>$ 0.85 can be achieved.

@@

In summary, we have
presented a comparative experimental and modeling study on macroscopic
salt rejection through a sheet of large-area porous graphene under
electrostatic gating. We show that due to a small quantum capacitance
of double layer graphene, the graphene surface potential is
considerably lower than the applied gate voltage. As a result, the
subtle redistribution of the electrochemical potentials create new
pathways for ionic transport, which in turn lead to a considerably
degree of salt rejection. We report a high degree of salt rejection at
$V_{\mathrm{G}}$ = 1.25 V of up to 55\% and 80\%, based on our
experiments and theoretical predictions, respectively. We demonstrate
that the observed salt rejection positively correlates with the Debye
screening length that nonlinearly modulates the graphene surface
potential and charge density. The experimental results and fundamental
principles presented here open an avenue towards realization of
atomically thin 2D porous membranes for advanced separation process in
electrolyte solutions.

@@

\begin{acknowledgement}
\todo[inline]{TBD} R.M.W. and H.G.P. acknowledge the support from
XXX. T.T. and C.J.S. are grateful for the financial support from the
ETH startup funding.
\end{acknowledgement}

@@

H.G.P and C.J.S conceived the experiments. R.M.W and K.Y. measured the ion
diffusion and gating experiments. T.T performed numerical
simulations. All authors contributed to writing and discussion.
